### 2018-02-07 submission/supplemental.Rmd
change the title
fix title
change to OR instead of RR

# Investigating the Microbiota and Colorectal Cancer: The Importance of Community

@@

**Table S3: Alpha Diversity Metrics RR in Tissue for Adenoma**

@@

alpha_RR_adn_tissue <- as.data.frame(read_csv("../data/process/tables/alpha_adn_RR_tissue_composite.csv")) %>% 
  mutate(rr = round(rr, digits = 2), 
         ci_lb = round(ci_lb, digits = 2), 
         ci_ub = round(ci_ub, digits = 2), 
         pvalue = round(pvalue, digits = 2), 
         measure = c("OTU Richness", "Shannon Diversity", "Evenness"))

colnames(alpha_RR_adn_tissue) <- c("Relative Risk", "Lower Bound", "Upper Bound", "P-value", "Measure")

@@

**Table S4: Alpha Diversity Metrics RR in Tissue for Unmatched Carcinoma Non-Carcinoma Samples**

@@

alpha_RR_crc_unmatch_tissue <- as.data.frame(read_csv("../data/process/tables/alpha_RR_unmatched_tissue_composite.csv")) %>%   mutate(rr = round(rr, digits = 2), 
         ci_lb = round(ci_lb, digits = 2), 
         ci_ub = round(ci_ub, digits = 2), 
         pvalue = round(pvalue, digits = 2), 
         measure = c("OTU Richness", "Shannon Diversity", "Evenness"))

colnames(alpha_RR_crc_unmatch_tissue) <- c("Relative Risk", "Lower Bound", "Upper Bound", "P-value", "Measure")

@@

**Table S5: Alpha Diversity Metrics RR in Tissue for Matched Carcinoma Non-Carcinoma Samples**

@@

alpha_RR_crc_match_tissue <- as.data.frame(read_csv("../data/process/tables/alpha_RR_matched_tissue_composite.csv")) %>% 
  mutate(rr = round(rr, digits = 2), 
         ci_lb = round(ci_lb, digits = 2), 
         ci_ub = round(ci_ub, digits = 2), 
         pvalue = round(pvalue, digits = 2), 
         measure = c("OTU Richness", "Shannon Diversity", "Evenness"))

colnames(alpha_RR_crc_match_tissue) <- c("Relative Risk", "Lower Bound", "Upper Bound", "P-value", "Measure")

@@

**Table S8: RR of Adenoma in Stool for each Individual Genera with Initial P-Value under 0.05**

@@

temp_8 <- read_csv("../data/process/tables/adn_select_genus_RR_stool_composite.csv") %>% 
  mutate(bh = p.adjust(pvalue, method = "BH")) %>% filter(pvalue < 0.05) %>% 
  arrange(bh, pvalue, rr) %>% 
  mutate(rr = round(rr, digits = 2), 
         ci_lb = round(ci_lb, digits = 2), 
         ci_ub = round(ci_ub, digits = 2), 
         pvalue = round(pvalue, digits = 4), 
         bh = round(bh, digits = 3), 
         measure = str_replace_all(measure, "_", " ")) %>% 
  select(rr, ci_lb, ci_ub, pvalue, bh, measure)

colnames(temp_8) <- c("RR", "Lower Bound", "Upper Bound", "P-value", "BH", "Lowest Genera ID")

@@

**Table S9: RR of Adenoma in Tissue for each Individual Genera with Initial P-Value under 0.05**

@@

temp_9 <- read_csv("../data/process/tables/adn_select_genus_RR_tissue_composite.csv") %>% 
  mutate(bh = p.adjust(pvalue, method = "BH")) %>% filter(pvalue < 0.05) %>% 
  arrange(bh, pvalue, rr) %>% 
  mutate(rr = round(rr, digits = 2), 
         ci_lb = round(ci_lb, digits = 2), 
         ci_ub = round(ci_ub, digits = 2), 
         pvalue = round(pvalue, digits = 4), 
         bh = round(bh, digits = 3), 
         measure = str_replace_all(measure, "_", " ")) %>% 
  select(rr, ci_lb, ci_ub, pvalue, bh, measure)

colnames(temp_9) <- c("RR", "Lower Bound", "Upper Bound", "P-value", "BH", "Lowest Genera ID")

@@

**Table S10: RR of Carcinoma in Stool for each Individual Genera with Initial P-Value under 0.05**

@@

temp_10 <- read_csv("../data/process/tables/select_genus_RR_stool_composite.csv") %>% 
  mutate(bh = p.adjust(pvalue, method = "BH")) %>% filter(pvalue < 0.05) %>% 
  arrange(bh, pvalue, rr) %>% 
  mutate(rr = round(rr, digits = 2), 
         ci_lb = round(ci_lb, digits = 2), 
         ci_ub = round(ci_ub, digits = 2), 
         pvalue = format(pvalue, scientific = T, digits = 3), 
         bh = format(bh, scientific = T, digits = 3), 
         measure = str_replace_all(measure, "_", " ")) %>% 
  select(rr, ci_lb, ci_ub, pvalue, bh, measure)

colnames(temp_10) <- c("RR", "Lower Bound", "Upper Bound", "P-value", "BH", "Lowest Genera ID")

@@

**Table S11: RR of Carcinoma in Tissue for each Individual Genera with Initial P-Value under 0.05**

@@

temp_11 <- read_csv("../data/process/tables/select_genus_RR_tissue_composite.csv") %>% 
  mutate(bh = p.adjust(pvalue, method = "BH")) %>% filter(pvalue < 0.05) %>% 
  arrange(bh, pvalue, rr) %>% 
  mutate(rr = round(rr, digits = 2), 
         ci_lb = round(ci_lb, digits = 2), 
         ci_ub = round(ci_ub, digits = 2), 
         pvalue = format(pvalue, scientific = T, digits = 3), 
         bh = format(bh, scientific = T, digits = 3), 
         measure = str_replace_all(measure, "_", " ")) %>% 
  select(rr, ci_lb, ci_ub, pvalue, bh, measure)

colnames(temp_11) <- c("RR", "Lower Bound", "Upper Bound", "P-value", "BH", "Lowest Genera ID")

>>>>

# Making Sense of the Noise: Leveraging Existing 16S rRNA Gene Surveys to Identify Key Community Members in Colorectal Tumors

@@

**Table S3: Alpha Diversity Metrics OR in Tissue for Adenoma**

@@

alpha_RR_adn_tissue <- as.data.frame(read_csv("../data/process/tables/alpha_adn_OR_tissue_composite.csv")) %>% 
  mutate(rr = round(rr, digits = 2), 
         ci_lb = round(ci_lb, digits = 2), 
         ci_ub = round(ci_ub, digits = 2), 
         pvalue = round(pvalue, digits = 2), 
         measure = c("OTU Richness", "Shannon Diversity", "Evenness"))

colnames(alpha_RR_adn_tissue) <- c("Odds Ratio", "Lower Bound", "Upper Bound", "P-value", "Measure")

@@

**Table S4: Alpha Diversity Metrics OR in Tissue for Unmatched Carcinoma Non-Carcinoma Samples**

@@

alpha_RR_crc_unmatch_tissue <- as.data.frame(read_csv("../data/process/tables/alpha_OR_unmatched_tissue_composite.csv")) %>%   mutate(rr = round(rr, digits = 2), 
         ci_lb = round(ci_lb, digits = 2), 
         ci_ub = round(ci_ub, digits = 2), 
         pvalue = round(pvalue, digits = 2), 
         measure = c("OTU Richness", "Shannon Diversity", "Evenness"))

colnames(alpha_RR_crc_unmatch_tissue) <- c("Odds Ratio", "Lower Bound", "Upper Bound", "P-value", "Measure")

@@

**Table S5: Alpha Diversity Metrics OR in Tissue for Matched Carcinoma Non-Carcinoma Samples**

@@

alpha_RR_crc_match_tissue <- as.data.frame(read_csv("../data/process/tables/alpha_OR_matched_tissue_composite.csv")) %>% 
  mutate(rr = round(rr, digits = 2), 
         ci_lb = round(ci_lb, digits = 2), 
         ci_ub = round(ci_ub, digits = 2), 
         pvalue = round(pvalue, digits = 2), 
         measure = c("OTU Richness", "Shannon Diversity", "Evenness"))

colnames(alpha_RR_crc_match_tissue) <- c("Odds Ratio", "Lower Bound", "Upper Bound", "P-value", "Measure")

@@

**Table S8: OR of Adenoma in Stool for each Individual Genera with Initial P-Value under 0.05**

@@

temp_8 <- read_csv("../data/process/tables/adn_select_genus_OR_stool_composite.csv") %>% 
  mutate(bh = p.adjust(pvalue, method = "BH")) %>% filter(pvalue < 0.05) %>% 
  arrange(bh, pvalue, rr) %>% 
  mutate(rr = round(rr, digits = 2), 
         ci_lb = round(ci_lb, digits = 2), 
         ci_ub = round(ci_ub, digits = 2), 
         pvalue = round(pvalue, digits = 4), 
         bh = round(bh, digits = 3), 
         measure = str_replace_all(measure, "_", " ")) %>% 
  select(rr, ci_lb, ci_ub, pvalue, bh, measure)

colnames(temp_8) <- c("OR", "Lower Bound", "Upper Bound", "P-value", "BH", "Lowest Genera ID")

@@

**Table S9: OR of Adenoma in Tissue for each Individual Genera with Initial P-Value under 0.05**

@@

temp_9 <- read_csv("../data/process/tables/adn_select_genus_OR_tissue_composite.csv") %>% 
  mutate(bh = p.adjust(pvalue, method = "BH")) %>% filter(pvalue < 0.05) %>% 
  arrange(bh, pvalue, rr) %>% 
  mutate(rr = round(rr, digits = 2), 
         ci_lb = round(ci_lb, digits = 2), 
         ci_ub = round(ci_ub, digits = 2), 
         pvalue = round(pvalue, digits = 4), 
         bh = round(bh, digits = 3), 
         measure = str_replace_all(measure, "_", " ")) %>% 
  select(rr, ci_lb, ci_ub, pvalue, bh, measure)

colnames(temp_9) <- c("OR", "Lower Bound", "Upper Bound", "P-value", "BH", "Lowest Genera ID")

@@

**Table S10: OR of Carcinoma in Stool for each Individual Genera with Initial P-Value under 0.05**

@@

temp_10 <- read_csv("../data/process/tables/select_genus_OR_stool_composite.csv") %>% 
  mutate(bh = p.adjust(pvalue, method = "BH")) %>% filter(pvalue < 0.05) %>% 
  arrange(bh, pvalue, rr) %>% 
  mutate(rr = round(rr, digits = 2), 
         ci_lb = round(ci_lb, digits = 2), 
         ci_ub = round(ci_ub, digits = 2), 
         pvalue = format(pvalue, scientific = T, digits = 3), 
         bh = format(bh, scientific = T, digits = 3), 
         measure = str_replace_all(measure, "_", " ")) %>% 
  select(rr, ci_lb, ci_ub, pvalue, bh, measure)

colnames(temp_10) <- c("OR", "Lower Bound", "Upper Bound", "P-value", "BH", "Lowest Genera ID")

@@

**Table S11: OR of Carcinoma in Tissue for each Individual Genera with Initial P-Value under 0.05**

@@

temp_11 <- read_csv("../data/process/tables/select_genus_OR_tissue_composite.csv") %>% 
  mutate(bh = p.adjust(pvalue, method = "BH")) %>% filter(pvalue < 0.05) %>% 
  arrange(bh, pvalue, rr) %>% 
  mutate(rr = round(rr, digits = 2), 
         ci_lb = round(ci_lb, digits = 2), 
         ci_ub = round(ci_ub, digits = 2), 
         pvalue = format(pvalue, scientific = T, digits = 3), 
         bh = format(bh, scientific = T, digits = 3), 
         measure = str_replace_all(measure, "_", " ")) %>% 
  select(rr, ci_lb, ci_ub, pvalue, bh, measure)

colnames(temp_11) <- c("OR", "Lower Bound", "Upper Bound", "P-value", "BH", "Lowest Genera ID")
